---
title: "midterm_project"
author: "Ningze Zu, Jiahao Xu, Andrew Zhang, Albert Ding"
date: 
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(knitr)
library(scales)
library(gridExtra)
baseball <- read.csv("baseball_weather.csv", header = T) %>% filter(X.1 != "@")
basketball <- read.csv("basketball_weather.csv", header = T)
baseball11 <- read.csv("baseball_weather.csv", header = T) %>% filter(X.1 != "@")
baseball <- select(baseball, Gm., Year, DATE, X, Tm, Opp, W.L, Win, Loss, Save, Time, D.N, Attendance, TAVG, TMAX, TMIN)
write.csv(baseball, file = "baseball00.csv")
```

```{r}
# There appears to be a weak but slightly positive relationship between  average temperature and attendance over the past six seasons
ggplot(baseball, mapping = aes(x = TAVG, y = Attendance)) +
  geom_point(mapping = aes(color = Year)) +
  geom_smooth() + 
  ggtitle("Average Temperature vs. Attendance (2012 - 2017)") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Average Temperature on Game Day (Degrees F)") + 
  ylab("Attendance")
```


```{r}
# 2017 Season
baseball_2017 <- baseball %>% filter(Year == 2017)
# Relationship between average temperature with attendance of season 2017
ggplot(baseball_2017, aes(TAVG, Attendance)) + 
  geom_point(color = "blue") + 
  geom_smooth(method = "lm", color = "red") + 
  ggtitle("Average Temperature vs. Attendance (2017)") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Average Temperature on Game Day (Degrees F)") + 
  ylab("Attendance")


# 2016 Season
baseball_2016 <- baseball %>% filter(Year == 2016)
# Relationship between average temperature with attendance of season 2016
ggplot(baseball_2016, aes(TAVG, Attendance)) + 
  geom_point(color = "blue") + 
  geom_smooth(method = "lm", color = "red") +
  ggtitle("Average Temperature vs. Attendance (2016)") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Average Temperature on Game Day (Degrees F)") + 
  ylab("Attendance")

# 2015 Season
baseball_2015 <- baseball %>% filter(Year == 2015)
# Relationship between average temperature with attendance of season 2015
ggplot(baseball_2015, aes(TAVG, Attendance)) + 
  geom_point(color = "blue") + 
  geom_smooth(method = "lm", color = "red") + 
  ggtitle("Average Temperature vs. Attendance (2015)") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Average Temperature on Game Day (Degrees F)") + 
  ylab("Attendance")

# 2014 Season
baseball_2014 <- baseball %>% filter(Year == 2014)
# Relationship between average temperature with attendance of season 2014
ggplot(baseball_2014, aes(TAVG, Attendance)) + 
  geom_point(color = "blue") + 
  geom_smooth(method = "lm", color = "red") + 
  ggtitle("Average Temperature vs. Attendance (2014)") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Average Temperature on Game Day (Degrees F)") + 
  ylab("Attendance")

# 2013 Season
baseball_2013 <- baseball %>% filter(Year == 2013)
# Relationship between average temperature with attendance of season 2013
ggplot(baseball_2013, aes(TAVG, Attendance)) + 
  geom_point(color = "blue") + 
  geom_smooth(method = "lm", color = "red") + 
  ggtitle("Average Temperature vs. Attendance (2013)") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Average Temperature on Game Day (Degrees F)") + 
  ylab("Attendance")
```

Conclusion: There appears to be a weak but slightly positive relationship between  average temperature and attendance over the past six seasons.

```{r}
# 2017
# Summary of attendance in seanson 2017 with different opponent.
# Group by different opponents and arrange the attendance from high to low
baseball_opp17 <- baseball_2017 %>% group_by(Opp) %>% summarise(avg_attendance = round(mean(Attendance),,digits = 0))
baseball_opp17 <- arrange(baseball_opp17, desc(avg_attendance))

ggplot(baseball_opp17, aes(Opp, avg_attendance)) + 
  geom_bar(stat = "identity") +
  ggtitle("Average Attendance vs. Opponents in 2017") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Opponent") + 
  ylab("Average Attendance") 


kable(baseball_opp17)


```

```{r}
# 2016
# Summary of attendance in seanson 2016 with different opponent.
# Group by different opponents and arrange the attendance from high to low
baseball_opp16 <- baseball_2016 %>% group_by(Opp) %>% summarise(avg_attendance = round(mean(Attendance),digits = 0))
baseball_opp16 <- arrange(baseball_opp16, desc(avg_attendance))

ggplot(baseball_opp16, aes(Opp, avg_attendance)) + 
  geom_bar(stat = "identity") +
  ggtitle("Average Attendance vs. Opponents in 2016") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Opponent") + 
  ylab("Average Attendance") 


kable(baseball_opp16)



```

```{r}
# 2015
# Summary of attendance in seanson 2016 with different opponent.
# Group by different opponents and arrange the attendance from high to low
baseball_opp15 <- baseball_2015 %>% group_by(Opp) %>% summarise(avg_attendance = round(mean(Attendance),digits = 0))
baseball_opp15 <- arrange(baseball_opp15, desc(avg_attendance))

ggplot(baseball_opp15, aes(Opp, avg_attendance)) + 
  geom_bar(stat = "identity") +
  ggtitle("Average Attendance vs. Opponents in 2015") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Opponent") + 
  ylab("Average Attendance") 


kable(baseball_opp15)

```

```{r}
# 2014
# Summary of attendance in seanson 2016 with different opponent.
# Group by different opponents and arrange the attendance from high to low
baseball_opp14 <- baseball_2014 %>% group_by(Opp) %>% summarise(avg_attendance = round(mean(Attendance),,digits = 0))
baseball_opp14 <- arrange(baseball_opp14, desc(avg_attendance))

ggplot(baseball_opp14, aes(Opp, avg_attendance)) + 
  geom_bar(stat = "identity") +
  ggtitle("Average Attendance vs. Opponents in 2014") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Opponent") + 
  ylab("Average Attendance") 


kable(baseball_opp14)


```

```{r}
# 2013
# Summary of attendance in seanson 2013 with different opponent.
# Group by different opponents and arrange the attendance from high to low
baseball_opp13 <- baseball_2013 %>% group_by(Opp) %>% summarise(avg_attendance = round(mean(Attendance),digits = 0))
baseball_opp13 <- arrange(baseball_opp13, desc(avg_attendance))

ggplot(baseball_opp13, aes(Opp, avg_attendance)) + 
  geom_bar(stat = "identity") +
  ggtitle("Average Attendance vs. Opponents in 2013")+
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Opponent") + 
  ylab("Average Attendance")


kable(baseball_opp13)
```

```{r}
# Summary of attendance in 6 seansons with different opponent.
# Group by different opponents and arrange the attendance from high to low
baseball_opp <- baseball %>% group_by(Opp) %>% summarise(avg_attendance = round(mean(Attendance),digits = 0))
baseball_opp <- arrange(baseball_opp, desc(avg_attendance))

ggplot(baseball_opp, aes(Opp, avg_attendance)) +
  geom_bar(stat = "identity") + ggtitle("Average Attendance vs. Opponents in Six Seasons") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Opponent") + 
  ylab("Average Attendance")

kable(baseball_opp)

```

Conclusion: Based on the bar plots, different opponents affect the average attendance of the baseball game.  
```{r}
# How the rain/snowy/windy days will affect the attendance of Red Sox, since base game is hypaethral.
baseball_SpecialWeather<- baseball11 %>% select(Gm.,Year,DATE, Tm, Time, Attendance,SNOW,PRCP )%>% filter(PRCP!=0)

# The rain influences on Red Sox attendence
plot1<-ggplot(baseball_SpecialWeather, aes(PRCP, Attendance)) + 
  geom_point(color = "blue") + 
  geom_smooth(method = "lm", color = "red") + 
  ggtitle("Precipitation vs. Attendance (2013-2017)") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Precipitation on Game Day (mm)") + 
  ylab("Total Attendance")

# The snow influences on Red Sox attendence
plot2<-ggplot(baseball_SpecialWeather, aes(SNOW, Attendance)) + 
  geom_point(color = "blue") + 
  geom_smooth(method = "lm", color = "red") + 
  ggtitle("Snow vs. Attendance (2013-2017)") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Whether snow on Game Day ") + 
  ylab("Total Attendance")

plot1
plot2

```

Conclusion: Rain has little influcences on attendence, but snow has obvious influcences on attendence.


```{r}
baseball_SpecialWeather17 <- baseball_SpecialWeather %>% filter(Year == 2017)
baseball_SpecialWeather16 <- baseball_SpecialWeather %>% filter(Year == 2016)
baseball_SpecialWeather15 <- baseball_SpecialWeather %>% filter(Year == 2015)
baseball_SpecialWeather14 <- baseball_SpecialWeather %>% filter(Year == 2014)
baseball_SpecialWeather13 <- baseball_SpecialWeather %>% filter(Year == 2013)

# Rain influences on Red Sox attendence in 2017:
plot17<-ggplot(baseball_SpecialWeather17, aes(PRCP, Attendance)) + 
  geom_point(color = "blue") + 
  geom_smooth(method = "lm", color = "red") + 
  ggtitle("Precipitation vs. Attendance (2017)") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Precipitation on Game Day (mm)") + 
  ylab("Total Attendance")

# The rain influences on Red Sox attendence in 2016:
plot16<-ggplot(baseball_SpecialWeather16, aes(PRCP, Attendance)) + 
  geom_point(color = "blue") + 
  geom_smooth(method = "lm", color = "red") + 
  ggtitle("Precipitation vs. Attendance (2016)") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Precipitation on Game Day (mm)") + 
  ylab("Total Attendance")

# The rain influences on Red Sox attendence in 2015:
plot15<-ggplot(baseball_SpecialWeather15, aes(PRCP, Attendance)) + 
  geom_point(color = "blue") + 
  geom_smooth(method = "lm", color = "red") + 
  ggtitle("Precipitation vs. Attendance (2015)") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Precipitation on Game Day (mm)") + 
  ylab("Total Attendance")

# The rain influences on Red Sox attendence in 2014:
plot14<-ggplot(baseball_SpecialWeather14, aes(PRCP, Attendance)) + 
  geom_point(color = "blue") + 
  geom_smooth(method = "lm", color = "red") + 
  ggtitle("Precipitation vs. Attendance (2014)") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Precipitation on Game Day (mm)") + 
  ylab("Total Attendance")

# The rain influences on Red Sox attendence in 2013:
plot13<-ggplot(baseball_SpecialWeather13, aes(PRCP, Attendance)) + 
  geom_point(color = "blue") + 
  geom_smooth(method = "lm", color = "red") + 
  ggtitle("Precipitation vs. Attendance (2013)") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Precipitation on Game Day (mm)") + 
  ylab("Total Attendance")

plot17
plot16
plot15
plot14
plot13
```

## Basketball 
```{r}
bball12 <- read.csv("attend2012.csv")
bball13 <- read.csv("attend2013.csv")
bball14 <- read.csv("attend2014.csv")
bball15 <- read.csv("attend2015.csv")
bball16 <- read.csv("attend2016.csv")

bball <- rbind(bball12, bball13, bball14, bball15, bball16)
bball$Year <- factor(bball$Year)
colnames(bball)[3] <- "Opp"
bball$Opp <- factor(bball$Opp)
write.csv(bball, file = "bball.csv")
#View(bball)
```

```{r}
ggplot(bball, mapping = aes(x = TAVG, y = Attendance)) +
  geom_point(mapping = aes(color = Year)) +
  geom_smooth() + 
  ggtitle("Average Temperature vs. Attendance (2012 - 2017)") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Average Temperature on Game Day (°F)") + 
  ylab("Attendance")
```


```{r}
# 2017 Season
bball_2017 <- bball %>% filter(Year == 2017)
# Relationship between average temperature with attendance of season 2017
ggplot(bball_2017, aes(TAVG, Attendance)) + 
  geom_point(color = "blue") + 
  geom_smooth(method = "lm", color = "red") + 
  ggtitle("Average Temperature vs. Attendance (2017)") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Average Temperature on Game Day (°F)") + 
  ylab("Attendance")


# 2016 Season
bball_2016 <- bball %>% filter(Year == 2016)
# Relationship between average temperature with attendance of season 2016
ggplot(bball_2016, aes(TAVG, Attendance)) + 
  geom_point(color = "blue") + 
  geom_smooth(method = "lm", color = "red") +
  ggtitle("Average Temperature vs. Attendance (2016)") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Average Temperature on Game Day (°F)") + 
  ylab("Attendance")

# 2015 Season
bball_2015 <- bball %>% filter(Year == 2015)
# Relationship between average temperature with attendance of season 2015
ggplot(bball_2015, aes(TAVG, Attendance)) + 
  geom_point(color = "blue") + 
  geom_smooth(method = "lm", color = "red") + 
  ggtitle("Average Temperature vs. Attendance (2015)") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Average Temperature on Game Day (°F)") + 
  ylab("Attendance")

# 2014 Season
bball_2014 <- bball %>% filter(Year == 2014)
# Relationship between average temperature with attendance of season 2014
ggplot(bball_2014, aes(TAVG, Attendance)) + 
  geom_point(color = "blue") + 
  geom_smooth(method = "lm", color = "red") + 
  ggtitle("Average Temperature vs. Attendance (2014)") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Average Temperature on Game Day (°F)") + 
  ylab("Attendance")

# 2013 Season
bball_2013 <- bball %>% filter(Year == 2013)
# Relationship between average temperature with attendance of season 2013

bball_2013$TAVG <- (bball_2013$TMAX + bball_2013$TMIN)/2
ggplot(bball_2013, aes(TAVG, Attendance)) + 
  geom_point(color = "blue") + 
  geom_smooth(method = "lm", color = "red") + 
  ggtitle("Average Temperature vs. Attendance (2013)") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Average Temperature on Game Day (°F)") + 
  ylab("Attendance")
```

Conclusion: There are no evident relationship between the average temperature and the attendace of these six seasons game. 

```{r}
# 2017
# Summary of attendance in seanson 2017 with different opponent.
# Group by different opponents and arrange the attendance from high to low
bball_opp17 <- bball_2017 %>% group_by(Opp) %>% summarise(avg_attendance = round(mean(Attendance),,digits = 0))
bball_opp17 <- arrange(bball_opp17, desc(avg_attendance))

ggplot(bball_opp17, aes(Opp, avg_attendance)) + 
  geom_bar(stat = "identity") +
  ggtitle("Average Attendance vs. Opponents in 2017") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Opponent") + 
  ylab("Average Attendance") 


knitr::kable(bball_opp17)
```

```{r}
# 2016
# Summary of attendance in seanson 2016 with different opponent.
# Group by different opponents and arrange the attendance from high to low
bball_opp16 <- bball_2016 %>% group_by(Opp) %>% summarise(avg_attendance = round(mean(Attendance),digits = 0))
bball_opp16 <- arrange(bball_opp16, desc(avg_attendance))

ggplot(bball_opp16, aes(Opp, avg_attendance)) + 
  geom_bar(stat = "identity") +
  ggtitle("Average Attendance vs. Opponents in 2016") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Opponent") + 
  ylab("Average Attendance") 


knitr::kable(bball_opp16)
```

```{r}
# 2015
# Summary of attendance in seanson 2016 with different opponent.
# Group by different opponents and arrange the attendance from high to low
bball_opp15 <- bball_2015 %>% group_by(Opp) %>% summarise(avg_attendance = round(mean(Attendance),digits = 0))
bball_opp15 <- arrange(bball_opp15, desc(avg_attendance))

ggplot(bball_opp15, aes(Opp, avg_attendance)) + 
  geom_bar(stat = "identity") +
  ggtitle("Average Attendance vs. Opponents in 2015") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Opponent") + 
  ylab("Average Attendance") 


knitr::kable(bball_opp15)
```

```{r}
# 2014
# Summary of attendance in seanson 2016 with different opponent.
# Group by different opponents and arrange the attendance from high to low
bball_opp14 <- bball_2014 %>% group_by(Opp) %>% summarise(avg_attendance = round(mean(Attendance),,digits = 0))
bball_opp14 <- arrange(bball_opp14, desc(avg_attendance))

ggplot(bball_opp14, aes(Opp, avg_attendance)) + 
  geom_bar(stat = "identity") +
  ggtitle("Average Attendance vs. Opponents in 2014") +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Opponent") + 
  ylab("Average Attendance") 


knitr::kable(bball_opp14)
```

```{r}
# 2013
# Summary of attendance in seanson 2013 with different opponent.
# Group by different opponents and arrange the attendance from high to low
bball_opp13 <- bball_2013 %>% group_by(Opp) %>% summarise(avg_attendance = round(mean(Attendance),digits = 0))
bball_opp13 <- arrange(bball_opp13, desc(avg_attendance))

ggplot(bball_opp13, aes(Opp, avg_attendance)) + 
  geom_bar(stat = "identity") +
  ggtitle("Average Attendance vs. Opponents in 2013")+
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Opponent") + 
  ylab("Average Attendance")


knitr::kable(bball_opp13)
```

```{r}
# Summary of attendance in 6 seansons with different opponent.
# Group by different opponents and arrange the attendance from high to low
bball_opp <- bball %>% group_by(Opp) %>% summarise(avg_attendance = round(mean(Attendance),digits = 0))
bball_opp <- arrange(bball_opp, desc(avg_attendance))

ggplot(bball_opp, aes(Opp, avg_attendance)) +
  geom_bar(stat = "identity") + ggtitle("Average Attendance vs. Opponents in Six Seasons") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  theme(axis.title.x = element_text(size = 14)) +
  theme(axis.title.y = element_text(size = 14)) +
  theme(plot.title = element_text(hjust = 0.5, size = 16)) +
  xlab("Opponent") + 
  ylab("Average Attendance")

knitr::kable(bball_opp)
```

```{r}
library(tidyverse)
basketball_WeatherAll<-read.csv("bball.csv")
basketball_SpecialWeather<- basketball_WeatherAll %>% select(Year,Date, Attendance,AWND,PRCP ) 

library(gridExtra)
plot1<-ggplot(basketball_SpecialWeather, aes(PRCP, Attendance)) + 
  geom_point(mapping=aes(color = Year)) + 
  geom_smooth() + 
  ggtitle("Precipitation vs. Attendance (2013-2017)") +
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab("Precipitation on Game Day (mm)") + 
  ylab("Total Attendance")
# The snow influences on Red Sox attendence
plot2<-ggplot(basketball_SpecialWeather, aes(AWND,Attendance)) + 
  geom_point(mapping=aes(color = Year)) + 
  geom_smooth() + 
  ggtitle("Wind vs. Attendance (2013-2017)") +
  theme(plot.title = element_text(hjust = 0.5)) +
  xlab("Whether snow on Game Day ") + 
  ylab("Total Attendance")
#grid.arrange(plot1,plot2,ncol=2)
plot1
plot2
```

